%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer - Core Services Team} % Job title
    {WINAMAX} % Organization
    {Paris, France} % Location
    {Jan. 2017 - Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a new team infrastructure on AWS, whose role is to provide internal facing services running on Docker with scaling and high-availability constraints in mind.}
        \item {Developed several microservices in Python for online gambling regulations and their integration with existing teams.}
        \item {Worked on the build system, deployment, logging, monitoring, metrics, alerting, and overall automation of the system, using several tools of the AWS stack (EC2, ECS, S3), and others such as Consul or Ansible.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Software Engineer - Poker Back-end Team} % Job title
    {WINAMAX} % Organization
    {Paris, France} % Location
    {Feb. 2016 - Jan. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on integrating Apache Kafka as a replacement for OpenAMQ brokers used between back-end services.}
        \item {Reworked several C++ services to increase reliability and performance using Kafka to reduce message loss.}
        \item {Maintained and worked on several improvements and bugfixes on the existing services.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administrator - Assistants' laboratory} % Job title
    {EPITA} % Organization
    {Paris, France} % Location
    {Jan. 2015 - Feb. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on the security, scalability and maintenance of the existing infrastructure.}
       	\item {Provided high-availability services to 300 students and 30 assistants.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Teaching Assistant in Computer Science} % Job title
    {EPITA} % Organization
    {Paris, France} % Location
    {Jan. 2015 - Jan. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught UNIX, shell, C, C++, Java, SQL and several design patterns to 300 students.}
        \item {Prepared, presented and corrected several projects, lessons and exams.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {.NET Software Developer Intern} % Job title
    {STELIA Aerospace - AIRBUS Group} % Organization
    {Saint-Nazaire, France} % Location
    {Aug. 2014 - Jan. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped provide useful tools while rewriting several programs from VB.NET to C\#, in order to facilitate the SI migration from Windows XP to Windows 7 in a safety critical environment.}
        \item {Developed several applications and tools for production planning, reporting and rewrote an entire legacy application in ASP.NET MVC.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {.NET Software Developer Intern} % Job title
    {THALES Electron Devices - THALES Group} % Organization
    {Vélizy-Villacoublay, France} % Location
    {Jun. 2013, Aug. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked at the Megajoule Laser Command Control Level 1.}
        \item {Developed C\# DLLs for XML/HDF5 data acquisition handling from one of the many Megajoule Laser power units.}
        \item {Implemented an equipment simulator GUI (WPF) with web services integration (WCF)}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
